---
title: "lastfmr"
output: github_document
---

[![Build Status](https://travis-ci.org/juyeongkim/lastfmr.svg?branch=master)](https://travis-ci.org/juyeongkim/lastfmr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/juyeongkim/lastfmr?branch=master&svg=true)](https://ci.appveyor.com/project/juyeongkim/lastfmr)
[![codecov](https://codecov.io/gh/juyeongkim/lastfmr/branch/master/graph/badge.svg)](https://codecov.io/gh/juyeongkim/lastfmr)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

`lastfmr` is an R interface to [Last.fm](http://www.last.fm/api). This is a port of Greg Hirson's [`RLastFM`](https://cran.r-project.org/package=RLastFM) (last updated 2010-08-10). There were some updates on API methods since his last update, so I added new methods and removed old ones. I also used json instead of xml.


## Get API Key

* [Create an API account](http://www.last.fm/api/account/create) from Last.fm Web Services
* Copy and save the API key somewhere safe


## Installation

```{r eval=FALSE, message=FALSE}
# install.packages("devtools")
devtools::install_github("juyeongkim/lastfmr")

library(lastfmr)
lastkey <- "YOUR_API_KEY_HERE"
```

```{r, echo=FALSE}
library(lastfmr)
lastkey <- lastfmr:::lastkey
```


## Examples

### Get user's top 5 artists

```{r}
top5 <- user_getTopArtists("platyjus", limit = 5, api_key = lastkey)

str(top5)

top5$artist$name
```


### Get album information
```{r}
fearfun <- album_getInfo("Father John Misty", "Fear Fun", api_key = lastkey)

str(fearfun)

fearfun$tracks$track[c("name", "duration")]
```


### Shiny App: lastfm explorer (work in progess)

https://juyeongkim.shinyapps.io/lastfm-explorer/
